### 2016-05-31 papers/thesis-vischer/Thesis.tex
fix reference bug in Brenden's thesis

\subsection{Hard Sphere}
The ``hard sphere'' is the simplest fluid model -- a hard sphere approximates a fluid particle as having no interactions other than collision. The only parameter for the hard sphere model is the sphere radius $\sigma$. The system is defined to have zero total linear momentum, and any collision between two or more spheres is perfectly elastic. Two spheres are not allowed to overlap, and else contribute nothing to the internal energy of the system. The energy between spheres $1$ and $2$, called the intermolecular pair potential, is then
\begin{equation} 
    \Phi_{12}(|\vec{r}|) = \begin{cases}\infty & |\vec{r}|\leq \sigma\\ 0 & |\vec{r}| > \sigma \end{cases}
\label{phi12hs}
\end{equation}
No attraction in Eq.~\ref{phi12hs}, and consequently no excess internal energy, implies that the excess free energy is purely entropic: 
\begin{align}
    F_{exc} &= -T S_{exc}
    \label{hs-fexc}
\end{align}
Eq.~\ref{hs-Fexc} showcases the beauty of the hard sphere system: one need only calculate the excess entropy of the hard sphere system to find the excess free energy.   
\subsubsection{Carnahan-Starling Equation of State}
We will need to compute the free energy of the a hard sphere system innumerable times throughout this work, and so we must make use of the Carnahan-Starling equation of state. shown in Eq.~\ref{C-S-eq}.
\begin{align}
    F_{exc}(\eta) &= N k_B T\,\frac{4\eta - 3\eta^2}{(1-\eta)^2}
    \label{C-S-eq}  
\end{align} 
where $\eta$ is the filling fraction, $N/V$. The Carnahan-Starling equation of state was developed to model hard spheres at low densities in the thermodynamic limit \cite{cs-eos}. We are very much concerned with cells significantly far from the thermodynamic limit. Thankfully, the Carnahan-Starling equation of state is still an excellent approximation at low to moderate filling fractions.\\

>>>>

\subsection{Hard Sphere}
The ``hard sphere'' is the simplest fluid model -- a hard sphere approximates a fluid particle as having no interactions other than collision. The only parameter for the hard sphere model is the sphere radius $\sigma$. The system is defined to have zero total linear momentum, and any collision between two or more spheres is perfectly elastic. Two spheres are not allowed to overlap, and else contribute nothing to the internal energy of the system. The energy between spheres $1$ and $2$, called the intermolecular pair potential, is then
\begin{equation} 
    \Phi_{12}(|\vec{r}|) = \begin{cases}\infty & |\vec{r}|\leq \sigma\\ 0 & |\vec{r}| > \sigma \end{cases}
\label{phi12hs}
\end{equation}
No attraction in Eq.~\ref{phi12hs}, and consequently no excess internal energy, implies that the excess free energy is purely entropic: 
\begin{align}
    F_{exc} &= -T S_{exc}
    \label{hs-fexc}
\end{align}
Eq.~\ref{hs-fexc} showcases the beauty of the hard sphere system: one need only calculate the excess entropy of the hard sphere system to find the excess free energy.
\subsubsection{Carnahan-Starling Equation of State}
We will need to compute the free energy of the a hard sphere system innumerable times throughout this work, and so we must make use of the Carnahan-Starling equation of state. shown in Eq.~\ref{C-S-eq}.
\begin{align}
    F_{exc}(\eta) &= N k_B T\,\frac{4\eta - 3\eta^2}{(1-\eta)^2}
    \label{C-S-eq}  
\end{align} 
where $\eta$ is the filling fraction, $N/V$. The Carnahan-Starling equation of state was developed to model hard spheres at low densities in the thermodynamic limit \cite{cs-eos}. We are very much concerned with cells significantly far from the thermodynamic limit. Thankfully, the Carnahan-Starling equation of state is still an excellent approximation at low to moderate filling fractions.\\
